\huge I don't know, are you sure we want to do this? Sea level adaptation decisions under uncertainty

### 2017-02-02 techreport/paper.tex
Updated readme files

%  ACKNOWLEDGMENTS
\section*{Acknowledgments}
This work was funded by NordForsk through project number 74456 ``Statistical Analysis of Climate Projections'' (eSACP) and The Research Council of Norway through project number 243953 ``Physical and Statistical Analysis of Climate Extremes in Large Datasets'' (ClimateXL). The source code for the analysis is implemented in the statistical programming language {\tt R} (\citet{R}) and is available on GitHub at \url{http://github.com/eSACP/SeaLevelDecisions/Code}.

>>>>

%  ACKNOWLEDGMENTS
\section*{Acknowledgments}
This work was funded by NordForsk through project number 74456 ``Statistical Analysis of Climate Projections'' (eSACP) and The Research Council of Norway through project number 243953 ``Physical and Statistical Analysis of Climate Extremes in Large Datasets'' (ClimateXL). The source code for the analysis is implemented in the statistical programming language {\tt R} (\citet{R}) and is available on GitHub at \url{http://github.com/eSACP/SeaLevelDecisions}.
